Predicting the Housing Market using \\ Linear Regression

### 2023-11-13 manuscript/Manuscript.tex
added comparison in application

Existing methods for predicting housing prices often rely on traditional statistical models that may struggle to capture the complexity and non-linear relationships present in real estate markets. Additionally, these models may not effectively incorporate the wide range of features that influence property values. An attractive solution would involve leveraging advanced machine learning techniques, such as multiple linear regression, to handle the complexity and non-linearity of the data. This allows the model to learn intricate patterns and relationships that may be challenging for traditional methods. Additionally, a comprehensive solution should consider factors such as location, economic indicators, property characteristics, and even social trends to build a more accurate and robust predictive model. The key is to strike a balance between model complexity and interpretability while ensuring it can effectively handle the diverse and dynamic nature of the real estate market.
% An overview of the topic
% Existing works
% Why are existing methods not sufficient? What are the elements of an attractive solution?
% Contributions
The main contribution of this paper is to corroborate the findings of prior research papers on this topic.

@@

The calculated R-squared value for the model was 0.6529. An R-squared value of 0.6529 indicates the proportion of the variance in the dependent variable that can be explained by the independent variables in a multiple linear regression model. In other terms, about 65.29\% of the variability in the observed data can be accounted for by the model.

>>>>

Existing methods for predicting housing prices often rely on traditional statistical models that may struggle to capture the complexity and non-linear relationships present in real estate markets. Additionally, these models may not effectively incorporate the wide range of features that influence property values. An attractive solution would involve leveraging advanced machine learning techniques, such as multiple linear regression, to handle the complexity and non-linearity of the data. This allows the model to learn intricate patterns and relationships that may be challenging for traditional methods. Additionally, a comprehensive solution should consider factors such as location, economic indicators, property characteristics, and even social trends to build a more accurate and robust predictive model. The key is to strike a balance between model complexity and interpretability while ensuring it can effectively handle the diverse and dynamic nature of the real estate market.
% An overview of the topic
% Existing works
% Why are existing methods not sufficient? What are the elements of an attractive solution?
% Contributions

The primary significance of this paper lies in its contribution to the existing body of knowledge on the specified topic. By corroborating the findings of prior research papers, this study aims to reinforce and validate the existing literature, thereby enhancing the robustness and reliability of the overall understanding of the field. Emphasize the specific aspects or insights where this paper aligns with or extends the conclusions drawn in previous research. In the final stages of our analysis, a crucial component involves a rigorous comparison between the model developed in this paper and the results available on \href{https://www.kaggle.com/code/ashydv/housing-price-prediction-linear-regression/notebook}{Kaggle}. The expected outcome is to try to produce a model that is more efficient than the one provided with the data set. By benchmarking our model against a Kaggle reference, we seek to evaluate its efficiency and effectiveness in predicting housing prices. This comparative analysis serves as a valuable validation step, allowing us to assess the model's performance in the context of real-world data and industry standards. The anticipated outcome of this comparative analysis is to identify areas of improvement and efficiency enhancement in our model when contrasted with the Kaggle benchmark. We aim not only to replicate but to surpass the predictive accuracy and performance metrics achieved by the existing Kaggle model.

@@

The calculated R-squared value for the model produced in this paper was 0.6529. A R-squared value of 0.6529 indicates the proportion of the variance in the dependent variable that can be explained by the independent variables in a multiple linear regression model. In other terms, about 65.29\% of the variability in the observed data can be accounted for by the model. The remaining 34.71\% of the variance is unaccounted for and may be attributed to other factors not included in your model or to random variability.

In comparison with the model produced in \href{https://www.kaggle.com/code/ashydv/housing-price-prediction-linear-regression/notebook}{Kaggle}, it is slightly better. The Kaggle model had a R-squared value of 0.5791. A R-squared value of 0.5791 suggests that approximately 57.91\% of the variance in the dependent variable can be explained by the independent variables in your regression model. The model that was produced in the paper has a better R-squared value of about 7.38\%.
